Hardware-accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-04-21 paper.tex
Removed old pseudocode for second approach
Included boolean diagrams in LaTeX file

@@

\begin{enumerate}
\item Render pieces from Boolean XOR behind intersection to framebuffer
\item Render intersection using Boolean AND to framebuffer
\item Render pieces from Boolean XOR in front of intersection to screen
\end{enumerate}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{boolean-and.pdf}
\caption{
Top down view of rendering intersecting volumes using the Boolean AND with depth
buffer masking approach.  First the part of the volume directly behind the
intersection, colored red, is rendered.  Next the intersection, colored green,
is rendered.  Then the the part of the volume directly in front of the
intersection, colored blue, is rendered.  Finally the depth buffer is masked off
using the intersection, and everything else, colored yellow, is rendered.
}
\label{boolean-and}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{boolean-xor.pdf}
\caption{
Rendering intersecting volumes using the Boolean AND with Boolean XOR approach.
First the pieces behind the intersection, colored red, are rendered.  Next the
intersection, colored green, is rendered.  Then the pieces in front of the
intersection, colored blue, are rendered.  A final pass renders the results to
the screen.
}
\label{boolean-xor}
\end{figure}
